A Switching Planner for Combined Task and Observation Planning

### 2010-11-29 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/intro.tex
shortened the introduction somewhat

Planning for agents acting in partially observable environments with
stochastic actions is extremely computationally
expensive~\cite{mdp-complexity}. Even relatively small partially
observable Markov decision problems (POMDPs), represented by tens of
propositional variables, produce state spaces far larger than existing
optimal or close to optimal planners can handle. For the easier
problem of planning in completely observable stochastic domains, an
alternative approach has been to use classical sequential planners and
replan when actions have unplanned-for outcomes~\cite{yoon:etal:2007}.
Execution monitoring tracks properties of the state that determine
whether a new plan is necessary. For partially observable domains,
only probabilistic information about such properties will, in general,
be available.

@@

This paper describes the planning component for a robotic system that
continuously deliberates in a stochastic dynamic environment in order
to achieve objectives set by the user, and acquire knowledge about its
surroundings. This domain features partial observability, particularly
because the state is not perfectly known, and state information is
gained by the robot through the use of unreliable sensing
actions. Using a propositionally factored state representation, for
interesting tasks the corresponding POMDP model is too large for a
POMDP solver to be applied directly. Inspired by the replanning
approaches used successfully for MDP
planning~\cite{yoon:etal:2007,yoon:etal:2008}, we propose an approach
that uses a replanning system to compute a reasonably valuable trace
in the model, and then uses a decision-theoretic planner on small
subproblems where reasoning about observations might be useful. We
refer to the complete system as a {\em switching continual
planner}. The approach is not optimal, particularly as it is based on
a satisficing sequential planner, but it performs better than the
sequential planner alone, and is fast enough to be used for real-time
decision-making on a mobile robot.

@@

The sequential planner we use is based
on \fastdownward~\cite{fast-downward}. We add the capability to
replan, and also allow agent knowledge to be represented explicitly,
so we can write actions that gain the agent knowledge. LEASE CITE
MICHAEL's WORK AS THE BASIS FOR THIS. For the decision-theoretic
planner we have implemented our own forward search in the belief-state
space.

Our switching planner gives us some important advantages in our
robotic domain. First, the significant source of uncertainty in the
domain is the unreliability of observations, and this approach is
particularly suited to problems that combine a deterministic task
planning problem with observations as the decision-theoretic planner
is only invoked to determine a characteristic of the underlying
state. Secondly, the replanning makes the system very robust to
changing objectives and the discovery of new facts about the world,
both of which are features of our domain.

>>>>

Planning for agents acting in partially observable environments with
stochastic actions is extremely computationally
expensive~\cite{mdp-complexity}. Even relatively small partially
observable Markov decision problems (POMDPs), represented by tens of
propositional variables, produce state spaces far larger than existing
optimal or close to optimal planners can handle. For the easier
problem of planning in completely observable stochastic domains, an
alternative approach has been to use classical sequential planners and
replan when actions have unplanned-for outcomes~\cite{yoon:etal:2007}.
Execution monitoring tracks properties of the state that determine
whether further planning is required. For partially observable
domains, only probabilistic information about such properties will, in
general, be available.

@@

This paper describes the planning component for a robotic system that
continuously deliberates in a stochastic dynamic environment in order
to achieve objectives set by the user, and acquire knowledge about its
surroundings. This domain features partial observability, particularly
because the state is not perfectly known, and state information is
gained by the robot through the use of unreliable sensing
actions. Using a propositionally factored state representation, for
interesting tasks the corresponding POMDP model is too large for a
POMDP solver to be applied directly. Inspired by the replanning
approaches used successfully for MDP
planning~\cite{yoon:etal:2007,yoon:etal:2008}, we propose a continual
planning approach that uses a classical planning system to compute a
reasonably valuable trace in the model, and then uses a
decision-theoretic planner on small subproblems where reasoning about
observations might be useful. We refer to the complete system as a
{\em switching continual planner}. The approach is not optimal,
particularly as it relies on the results of sequential planning
directly. It does nevertheless perform better than a purely sequential
replanner, and is fast enough to be used for real-time decision-making
on a mobile robot.

%% Switching gives us some important advantages in our robotic
%% domain. First, the significant source of uncertainty in the domain is
%% the unreliability of observations, and this approach is particularly
%% suited to problems that combine a deterministic task planning problem
%% with observations as the decision-theoretic planner is often invoked
%% to determine a characteristic of the underlying state. Secondly,
%% replanning makes our system robust to changing objectives and the
%% discovery of new facts about the world.

@@

%% The sequential planner we use is based
%% on \fastdownward~\cite{fast-downward}. We add the capability to replan
%% ~\cite{brenner:nebel:jaamas09}, and also allow agent
%% knowledge to be represented explicitly, so we can write actions that
%% gain the agent knowledge. LEASE CITE MICHAEL's WORK AS THE BASIS FOR
%% THIS. For the decision-theoretic planner we have implemented our own
%% forward search in the belief-state space.
